\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}

\name{Aaron}{Shenny}
\email{aaron.shenny@linkedin.com}
\phone{Kakkanad, India}


\begin{document}
\makecvtitle

\section{Summary}
Aspiring Software Engineer and MCA candidate with a strong focus on AI-driven automation and large-scale system development. Proficient in Python, Java, and C++, with a deep interest in Data Structures, Algorithms, and Distributed Systems. Certified in Google AI Agent development and recognized for technical excellence in hackathons and tech symposiums.

\section{Experience}
\cventry{October 2025 - November 2025}{Campus Ambassador}{Perplexity}{}{}{Led community engagement initiatives focusing on AI-driven search and information retrieval technologies. Facilitated technical discussions on natural language processing and agentic automation within the student community. Acted as a bridge between the developer community and product teams to provide feedback on tool usability and feature sets.}
\cventry{2024 - Present}{AI Agent Developer & Automation Specialist}{Self-Directed Projects / Google AI Intensive}{}{}{Developed autonomous agents using Google Agent Development Kit (ADK) and Google Gemini to automate complex software workflows. Focused on building scalable, efficient code for agentic automation, demonstrating a strong grasp of software architecture and system health. Implemented custom tools for data analysis and visualization using AI frameworks.}
\cventry{2024}{Technical Lead / Participant}{Krithi TechXodia & Cross Roads}{}{}{Competed in high-level tech symposiums, focusing on problem-solving through coding and system design. Collaborated with teams to develop software solutions under tight deadlines, emphasizing code accuracy, testability, and efficient debugging. Awarded for innovative approaches to technology-driven challenges.}

\section{Education}
\cventry{June 2025 - March 2030}{Master of Computer Applications - MCA (Integrated)}{Rajagiri College of Social Sciences}{}{}{}
\cventry{June 2012 - March 2025}{12th Grade - Higher Secondary Education}{Mar Thoma Public School}{}{}{}

\section{Skills}
\cvitem{}{Python, Java, C++, Data Structures & Algorithms, Google Gemini, Google Agent Development Kit (ADK), Agentic Automation, Distributed Systems Concepts, Software Test Engineering, System Debugging, Git, Large-scale Infrastructure Concepts}

\end{document}
